Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-01-12 ForegroundSimulations/ms.tex
Include figures under appropriate sections
From 4deee37 (master):
=====================

In ms.tex,

(*) Include figures under appropriate sections

@@

@@

@@

>>>>

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{off-axis_point_source_beam_chromaticity.eps}
\caption{Chromaticity of antenna power pattern at directions off-axis. }
\label{fig:off-axis-beam-chromaticity}
\end{figure*}

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{directional_high_delay_average_in_beam.eps}
\caption{All-sky directional chromaticity of antenna power pattern. }
\label{fig:directional-beam-chromaticity}
\end{figure*}

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{asm_beam_chromaticity_subband_150_MHz.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra. }
\label{fig:asm-dps-beam-chromaticity}
\end{figure*}

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast.eps}
\caption{Attenuation of foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power.}
\label{fig:fg-reflections}
\end{figure*}
